---
title: "QUANTIFY THE INFLUENCE OF UNEMPLOYMENT ON  ADULT OBESITY "
author: "Dee Muralidharan"
date: "July 28, 2017"
output: html_document
---

## Capstone Project

	This project is intended to study the causal relationship between unemployment and obesity. Two data sets will be utilized to perform this study.  The project is intended for law-makers , health advocates, public policy planners and anyone interested in this causal relationship. The project will study the data to answer the questions below 

```{r}
install.packages("dplyr")
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggmap)
library(zipcode)
library(mapproj)
library(RDSTK)
library(reshape)
library(data.table)
library(stats)
library(MASS)

```

##File Diabetes Prevelance

Read the file "Diabetes prevelance.csv" and clean up to confirm with the obesity file. 

```{r}

diabetes_prevelance <- read.csv("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/Diabetes prevelance.csv", header = TRUE, stringsAsFactors = FALSE)

## Remove rows with no data, Melt data into one big group such that all the columns are converted to rows and are listed as sub-categories. This set of code is used to factorise all the data in the Diabetes prevelance File
diabetes_prevelance1 <- diabetes_prevelance %>% select(-contains("limit")) %>% filter(number.2004 != ("No Data"))
diabetes_prevelance1<- melt (diabetes_prevelance1, id.var=1:3)
## Filter rows that have NA and rows that contain x.1
diabetes_prevelance1<- diabetes_prevelance1 %>% filter(variable != ("X.1")) %>% filter(variable != ("X"))
write.csv(diabetes_prevelance1, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/diabetes_prevelance1.csv")

```
 


```{r}


```

        In this section the next file will be sorted is the "leasiure_time_phy_inactivity.csv". The first part of the challenge is to remove all the NA and rows with "no data"

```{r}
setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")
leasiure_time_phy_in <- read.csv("leasiure_time_phy_inactivity.csv", header = TRUE, stringsAsFactors = FALSE)
## Remove columns that contain "confidence limit"
leasiure_time_phy_in <- leasiure_time_phy_in %>% select(-contains("confidence.limit")) %>% filter(number.2004 != ("No Data")) %>%  filter(percent.2009 != ("No Data"))
leasiure_time_phy_in <- melt (leasiure_time_phy_in, id.var=1:3)
write.csv(leasiure_time_phy_in, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/leasiure_time_phy_in.csv")

```

In the next set of codes the file that will be used to sort out the obesity prevelance in all the states

```{r}
setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")
ob_prev_all_states <- read.csv("ob_prev_all_states.csv", header = TRUE, stringsAsFactors = FALSE)
ob_prev_all_states <- ob_prev_all_states %>% filter(number.2004 != "No Data") %>%filter(percent.2009 != ("No Data")) %>%  select(-contains("confidence.limit"))
ob_prev_all_states <- melt (ob_prev_all_states, id.var=1:3)
write.csv(ob_prev_all_states, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/ob_prev_all_states.csv")
```

Now in this data set the unemployment file would be filtered for all years from 2004 to 2013 and the rest of the data would be discarded.

```{r}
## Import uemployment master file 
unemployment <- read.csv("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/u_employ_file.csv", header = TRUE, stringsAsFactors = FALSE)
##Remove the years 1993-2003 and the years above 2013
unemployment <- unemployment %>% filter(between (Year,2004, 2013))
# Compute mean unemployment for each year
unemployment <- aggregate(Rate ~ Country + State + County +Year, unemployment, mean)
# round the mean values
unemployment$Rate <- round(unemployment$ Rate,2)
write.csv(unemployment, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/unemployment.csv")
```


#Exploratory Analysis
Let Us work on the Expolaratory portion of this data to decide what may be required to gain more insight

```{r}
plot_diabetes_prevelance<- read.csv("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/diabetes_prevelance1.csv", header = TRUE, stringsAsFactors = FALSE )

plot_diabetes_prevelance <- separate(plot_diabetes_prevelance,variable,c("Variable", "Year"), sep = "[$[\\.]]", remove = TRUE )
write.csv(plot_diabetes_prevelance, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/plot_diabetes_prevelance.csv")
##Check for Normal distribution of the 
```

