---
title: "QUANTIFY THE INFLUENCE OF UNEMPLOYMENT ON  ADULT OBESITY "
author: "Dee Muralidharan"
date: "July 28, 2017"
output: html_document
---

## Capstone Project

	This project is intended to study the causal relationship between unemployment and obesity. Two data sets will be utilized to perform this study.  The project is intended for law-makers , health advocates, public policy planners and anyone interested in this causal relationship. The project will study the data to answer the questions below 

-	Impact of Geography and hence the weather on obesity (warm vs. cold)- 
-	Does areas with lower unemployment fare better in obesity prevention (i.e. economic demographics)
-	Does political inclinations change skew the relationship (Democratic vs. Republican) 
-	Does occupation i.e. service based vs. labor alter the obesity 
-	Which sex is more affected by unemployment?
-	What race is more affected by unemployment?


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggmap)
library(zipcode)
library(mapproj)
library(RDSTK)
```

##Step 1- Cleanup the 0besity_file
### Coldest vs Warmest

Climate effects on obesity will be studied and to ensure a fair comparison, states will be picked that are similar in all other aspects BUT climate. After looking at the data from the 48 states, Nebraska and North Dakota have very similar attributes but are different in the climatic conditions . 
The factors that require to be similar are Unemployment, Racial Demographics & dietary habits 
1. Unemployment rate Nebraska (Average unemployment rate) = 3.10 and North Dakota - 3.84-Very similar
2. Demographics - Racial mixture should be similar-Nebraska -86% white, N. Dakota - 90% white
3. Political leanings- Both states have conservative views and have consistently picked republican candidates in the previous five presidential elections. The political leanings and racial demographics are vital in establishing that Anglo-Saxon dietary and lifestyle preference are practiced by most of the people.  

 
```{r}
setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")
obesity_file <- read.csv ("obesity.csv", header=TRUE, stringsAsFactors = FALSE)


```

##High Level Summary of the actions 
- Remove all obesity values that have a blank in them and replace them with a NA
- Filter Data based on just the obese and overweight by each state 
-Filter Data to reflect Nebraska and North Dakota
- Change names of Columns - Data_Value and YearEnd to Percent_Of_Popul and Year respectively. 

```{r}
setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")

obesity_file <- obesity_file  %>% mutate ( #Change Blanks to NA in the whole file 
                                        Data_Value = replace( Data_Value , is.na(Data_Value), NA ))


cld_vs_wrm <- obesity_file%>% filter(!is.na(Data_Value)) %>% 
  
  filter (grepl("Percent of adults aged 18 years and older who have obesity",Question)
          
          | grepl("Percent of adults aged 18 years and older who have an overweight classification",Question))

cld_vs_wrm <- cld_vs_wrm %>% filter(grepl("NE", LocationAbbr)| grepl("ND", LocationAbbr))
cld_vs_wrm <- cld_vs_wrm %>% mutate(Weight_status = ifelse (grepl("Percent of adults aged 18 years and older who have obesity", Question), "Obese", "Overweight"))
colnames(cld_vs_wrm)[names(cld_vs_wrm) == 'Data_Value'] <- "Percent_Of_Popul"
colnames(cld_vs_wrm)[names(cld_vs_wrm) == 'YearEnd'] <- "Year"
write.csv(cld_vs_wrm,"obesity1.csv")
```

## Exploratory Plots 

  This portion we will look at trends with the Data filtered above, the purpose of the plot is exploratory and is intended to gain the big picture. 
  

```{r}

ggplot(cld_vs_wrm, aes(x =Year, y = Percent_Of_Popul, col = Weight_status
 )) + geom_point(size = 3, alpha = 0.5, position = position_jitterdodge (jitter.width = 0.5,dodge.width = 0.75)) + facet_grid(.~LocationDesc)+  theme_minimal()
```

  It can be Visualized that the data spread is evenly (between 25% to 45%) in both Nebraska and North Dakota which would be sufficient to conclude that Climatic conditions and thus geographical locations do not effect obesity significantly. However the outliers at both at the 45 and above and 25 and below are presenting an interesting story. It would be benefetial to check the unemployment in these counties. 

```{r}

setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")

cld_vs_wrm <- cld_vs_wrm %>% filter((Percent_Of_Popul > 40)| (Percent_Of_Popul < 25))

unemploy <- read.csv ("u_employ_file.csv", header=TRUE, stringsAsFactors = FALSE)

unemploy<- unemploy %>% unite(Address, County,State, Country,sep = ",", remove = FALSE)
year_filter <- c("2011", "2012", "2013", "2014", "2015" , "2016")
keep_states <- c("North Dakota" ,"Nebraska")
unemploy <- unemploy %>% filter(grepl(year_filter, Year)) %>% filter(grepl(keep_states,State))

## lat_long <-  mutate_geocode(unemploy, Address)
map_ND <- get_map (location = "North_Dakota,USA", , zoom = 7, source="google",maptype = "roadmap", crop= TRUE)

ggmap(map_ND) +  geom_point(lat_long, aes(x = lon, y = lat, alpha = .1, color= "Rate" ))+ scale_color_brewer(type = "seq", palette = 1)
write.csv(lat_long,"unemploy2.csv")
```




