---
title: "QUANTIFY THE INFLUENCE OF UNEMPLOYMENT ON  ADULT OBESITY "
author: "Dee Muralidharan"
date: "July 28, 2017"
output: html_document
---

## Capstone Project

	This project is intended to study the causal relationship between unemployment and obesity. Two data sets will be utilized to perform this study.  The project is intended for law-makers , health advocates, public policy planners and anyone interested in this causal relationship. The project will study the data to answer the questions below 

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggmap)
library(zipcode)
library(mapproj)
library(RDSTK)
library(reshape)
library(data.table)
```

##File Diabetes Prevelance

Read the file "Diabetes prevelance.csv" and clean up to confirm with the obesity file. 

```{r}
setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")

diabetes_prevelance <- read.csv("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/Diabetes prevelance.csv", header = TRUE, stringsAsFactors = FALSE)

diabetes_prevelance
```
 
Remove rows with no data, Melt data into one big group such that all the columns are converted to rows and are listed as sub-categories. This set of code is used to factorise all the data in the Diabetes prevelance File

```{r}
diabetes_prevelance1<- diabetes_prevelance %>% filter(number.2004 != ("No Data"))
diabetes_prevelance1 <- diabetes_prevelance1 %>% select(-contains("confidence.limit"))
write.csv(diabetes_prevelance1, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/diabetes_prevelance1.csv")
diabetes_prevelance1<- melt (diabetes_prevelance1, id.var=1:4)
## Filter rows that have NA and rows that contain x.1
diabetes_prevelance1<- diabetes_prevelance1 %>% filter(variable != ("X.1")) %>% select (-contains("X"))
write.csv(diabetes_prevelance1, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/diabetes_prevelance1.csv")
```

In this section the next file will be sorted is the "leasiure_time_phy_inactivity.csv".

```{r}
setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")
leasiure_time_phy_in <- read.csv("leasiure_time_phy_inactivity.csv", header = TRUE, stringsAsFactors = FALSE)
## Remove columns that contain "confidence limit"
leasiure_time_phy_in <- leasiure_time_phy_in %>% select(-contains("confidence.limit")) %>% filter(number.2004 != ("No Data")) %>%  filter(percent.2009 != ("No Data"))
leasiure_time_phy_in <- melt (leasiure_time_phy_in, id.var=1:4)
write.csv(leasiure_time_phy_in, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/leasiure_time_phy_in.csv")

```

