---
title: "QUANTIFY THE INFLUENCE OF UNEMPLOYMENT ON  ADULT OBESITY "
author: "Dee Muralidharan"
date: "July 28, 2017"
output: html_document
---

## Capstone Project

	This project is intended to study the causal relationship between unemployment and obesity. Two data sets will be utilized to perform this study.  The project is intended for law-makers , health advocates, public policy planners and anyone interested in this causal relationship. The project will study the data to answer the questions below 

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggmap)
library(zipcode)
library(mapproj)
library(RDSTK)
library(reshape)
library(data.table)
```

##File Diabetes Prevelance

Read the file "Diabetes prevelance.csv" and clean up rows that have 

```{r}
setwd("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive")

diabetes_prevelance <- read.csv("D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/Diabetes prevelance.csv", header = TRUE, stringsAsFactors = FALSE)

diabetes_prevelance
```
 
Remove rows with no data
```{r}
diabetes_prevelance1<- diabetes_prevelance %>% filter(number != ("No Data"))
diabetes_prevelance1 <- diabetes_prevelance1 %>% select(-contains("confidence.limit"))
setnames(diabetes_prevelance1, old=c("number.1","number.2","number.3","number.4","number.5","number.6","number.7","number.8","number.9"),new= c("number","number","number","number","number","number","number","number","number"))
setnames(diabetes_prevelance1, old=c("age.adjusted.percent.1","age.adjusted.percent.2","age.adjusted.percent.3","age.adjusted.percent.4","age.adjusted.percent.5","age.adjusted.percent.6","age.adjusted.percent.7","age.adjusted.percent.8", "age.adjusted.percent.9"),new=c("age.adjusted.percent","age.adjusted.percent","age.adjusted.percent","age.adjusted.percent","age.adjusted.percent","age.adjusted.percent","age.adjusted.percent","age.adjusted.percent","age.adjusted.percent" ))
setnames(diabetes_prevelance1, old=c("percent.1","percent.2","percent.3","percent.4","percent.5","percent.6","percent.7","percent.8","percent.9"),new= c("percent","percent","percent","percent","percent","percent","percent","percent","percent"))
##write.csv(diabetes_prevelance1, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/diabetes_prevelance1.csv")

diabetes_prevelance1<- melt (diabetes_prevelance1, id.var=1:4)
##diabetes_prevelance1 <- melt(diabetes_prevelance1,id= 1:4, measured = c("number",	"percent", 	"age.adjusted.percent",	"number","percent",	"age.adjusted.percent"))
write.csv(diabetes_prevelance1, "D:/springboard Data science/Capstone Project/Final Pick/Rmarkdown Home Drive/R write/diabetes_prevelance1.csv")
```

